\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}

### 2022-08-18 lin-vs-cen.tex
Vida's comments
Small typo fix

To prove \cref{kun_obrien_general}, \citet{kun.obrien.ea:polynomial} establish the critical role that lower bounds on the linear linear chromatic number of pseudogrids and subcubic trees play in establishing an upper bound on $\chicen(G)$ as a function of $\chilin(G)$. In their work, they establish (asymptotically) tight lower bounds for the linear chromatic number of subcubic trees, but their lower bounds for pseudogrids are not tight.

@@

  \item Points~1 and 2 demonstrate that in order to establish \cref{kun_obrien_general}, a lower bound on the linear chromatic number of a $\Omega(k^2)\times\Omega(k^2)$ grid minor (i.e., pseudogrid) is needed.  \citet[Lemma~5]{kun.obrien.ea:polynomial} establish such a lower bound. Specifically, they show that, if $G$ contains a $\Omega(k^2)\times \Omega(k^2)$ grid minor, then $\chilin(G)\in\Omega(k)$.
  In the current work, we spend considerable effort to prove the following tight bound:
\end{enumerate}

>>>>

To prove \cref{kun_obrien_general}, \citet{kun.obrien.ea:polynomial} establish the critical role that lower bounds on the linear chromatic number of pseudogrids and subcubic trees play in establishing an upper bound on $\chicen(G)$ as a function of $\chilin(G)$. In their work, they establish (asymptotically) tight lower bounds for the linear chromatic number of subcubic trees, but their lower bounds for pseudogrids are not tight.

@@

  \item Points~1 and 2 demonstrate that in order to establish \cref{kun_obrien_general}, a lower bound on the linear chromatic number of a $\Omega(k^2)\times\Omega(k^2)$ grid minor (i.e., pseudogrid) is needed.  \citet[Lemma~5]{kun.obrien.ea:polynomial} establish such a lower bound. Specifically, they show that, for any $\Omega(k^2)\times \Omega(k^2)$ pseudogrid $G$, $\chilin(G)\in\Omega(k)$.
  In the current work, we spend considerable effort to prove the following tight bound:
\end{enumerate}
